--- 
title: Live Systematic Review
subtitle: | 
  Functional Magnetic Resonance Imaging Studies Drug Cue-Reactivity (FDCR)
  Studies in Addiction Medicine
# author: "Mohsen Ebrahimi"
date: "2023-01-08"
site: bookdown::bookdown_site
documentclass: book
bibliography: ./bib/references.bib
url: https://mohsenebrahimyir.github.io/fdcr/
# favicon: 
#   - img/favicon.ico
# cover-image:
#   - img/cover.jpg
description: |
  Functional Magnetic Resonance Imaging Studies Drug Cue-Reactivity (FDCR)
  Studies in Addiction Medicine
link-citations: yes
linkcolor: blue
github-repo: mohsenebrahimyir/fdcr
classoption: openany
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	fig.align = "center",
	fig.pos = "!ht",
	# fig.id = FALSE,
	# fig.lp = NA,
	message = FALSE,
	warning = FALSE,
	out.width = "95%"
)
```

```{r include=FALSE}
source("R/library.R")
source("R/database.R")

unlink("docs", recursive = TRUE)
```

# Summary

In the last 25 years, hundreds of fMRI drug cue-reactivity (FDCR) studies in people with substance use disorders (SUDs) have formed an extensive body of evidence characterizing the neural substrates of cue-reactivity. However, no FDCR-derived biomarkers have yet obtained FDA approval for treatment development or clinical adoption. Traversing this translational gap requires a systematic assessment of the available evidence, mapping the methodological heterogeneity of FDCR, and an evaluation of possible clinical uses of FDCR-derived biomarkers. This page presents a live systematic review of the design aspects and methodological characteristics of FDCR studies and an overview of the extant research in the form of a scoping review
